\Huge \bf \sc Calibration of an inertial measurement unit

### 2013-07-11 latex/paper_sensores/paper.tex

As it was stated before, there exist many error sources in MEMS devices. In \cite{bib:calib_imu} two of this sources are mentioned: the nonlinear response of the sensors and the non-orthogonality of the axis of the sensor. In addition we can observe also that it exist an electric noise in the measures (figure \ref{fig:ruido}) and a dependance of the temperature.\\

@@

\subsection{Accelerometer}
Due to construction issues the sensibility axis of the device are generaly not orthogonals. Lets define a platform system as shown in figure \ref{fig:mongoose}Let $\mathbf{a}^a$ be the acceleration measured by the accelerometer and let $\mathbf{a}^p$ the acceleration measured in the platform system. We model this fact by the following linear transformation between the two acceleration vectors:

\begin{equation}
\mathbf{a}^p = \mathbf{T}_a^p\mathbf{a}^a, \; \mathbf{T}_a^p = \left(\begin{array}{ccc}
1 & - \alpha_{yz} & \alpha_{zy}\\
\alpha_{xz} & 1 & - \alpha_{zx}\\
-\alpha_{xy} & \alpha_{yx} & 1
\end{array}\right)
\end{equation}

\subsection{Gyroscope}

\section{Calibration method proposed}
\subsection{Static Parameter Calibration}
\subsubsection{Temperature adjust}

>>>>

As it was stated before, there exist many error sources in MEMS devices. In \cite{bib:calib_imu} two of this sources are mentioned: the nonlinear response of the sensors and the non-orthogonality of the axis of the sensor. In addition we can observe also that it exist an electric noise in the measures (figure \ref{fig:ruido}) and a dependance of the temperature.\\
\vspace{-10pt}
\begin{figure}[h!]
  \centering
  \subfloat[Accelerometer data $\hat{k}$]{\label{fig:angulos_1}
  		\includegraphics[width=1\columnwidth]
  			{./pics_paper/acc_noise.pdf}}\\[-5pt]
  			\vspace{-5pt}
  \subfloat[Gyroscope data $\hat{j}$]{\label{fig:angulos_2} 
  		\includegraphics[width=1\columnwidth]
  			{./pics_paper/gyro_noise.pdf}}
  \caption{Measures from accelerometer and gyroscope in static equilibrium}
  \label{fig:noise}
\end{figure}

@@

\subsection{Accelerometer}
Due to construction issues the sensitivity axis of the device are generaly not orthogonals. Lets define a platform system as shown in figure \ref{fig:mongoose}. Let $\mathbf{a}^a$ be the true acceleration expressed in the sensitivity axis of the accelerometer and let $\mathbf{a}^p$ be the true acceleration expressed in the platform system. We model this fact by the following linear transformation between the two acceleration vectors:

\begin{equation}
\mathbf{a}^p = \mathbf{T}_a^p\mathbf{a}^a, \; \mathbf{T}_a^p = \left(\begin{array}{ccc}
1 & - \alpha_{yz} & \alpha_{zy}\\
\alpha_{xz} & 1 & - \alpha_{zx}\\
-\alpha_{xy} & \alpha_{yx} & 1
\end{array}\right)
\label{eq:nonorto}
\end{equation}

In equation \ref{eq:nonorto}, scalars $\alpha_{ij}$ represents the rotation of the $i-th$ sensitivity axis of the acelerometer over the $j-th$ axis of the platform system. In figure \ref{fig:nonorto} this relation can be observed graphically. Since those errors are due to the manufacturing process we will assume that they will remain constant long enough.

\begin{figure}
	\centering
	\includegraphics[width=.6\columnwidth]{./pics_paper/ejes_acc.jpg}
	\caption{\textbf{Rotations of the sensitivity axis of the accelerometer over the axis of the platform system.}}
	\label{fig:nonorto}
\end{figure}

As it was stated befor, we are considering a linear model between the accleration measured in the sensitivity axis and the true acceleration in the same system. Thus we have:

\begin{equation}
\tilde{\mathbf{a}}^a = \mathbf{K}_a\mathbf{a}^a + \mathbf{b}_a
\label{eq:modlineal}
\end{equation}

In equation \ref{eq:modlineal}, $\tilde{\mathbf{a}}^a$ is the measure obtained by the accelerometer, $\mathbf{K}_a$ is a diagonal matrix that represents the sensitivity of each axis and $\mathbf{b}_a$ is a vector that represent the bias of each axis. Those parameters may variate as the temperature changes. However, in this stage we are going to consider them constant. Using equations \ref{eq:nonorto} and \ref{eq:modlineal} we can stablish a model of the acelerometer:

\begin{equation}
\tilde{\mathbf{a}}^a = \mathbf{K}_a\mathbf{T}_p^a\mathbf{a}^p + \mathbf{b}_a = \mathbf{K}_a(\mathbf{T}_a^p)^{-1}\mathbf{a}^p + \mathbf{b}_a 
\end{equation}

\subsection{Gyroscope}
The error sources consider in the case of the gyroscope are the same that we developed for the acclerometer. Thus, we are going to consider the same model:

\begin{equation}
\tilde{\mathbf{\omega}}_a = \mathbf{K}_{\omega}(\mathbf{T}_{\omega}^p)^{-1}\mathbf{\omega}^p+\mathbf{b}_{\omega}
\end{equation}
%TODO Poner en negrita los omega

\section{Calibration method proposed}
The problem of calibration is to establish the values for the unkwnown parameters of the model that adjust ``the better'' a certain set of data. This criterium will be defined in section \ref{sec:param}. For each sensor we want to estimate 12 parameters. We choose to make 27 different measures of accleration and angular speed (this actually means that we have 81 different values) and use 14 of this measures as a training set and the other 13 as a test set.

\subsection{Static Parameter Calibration}
\label{sec:param}

Let $\mathbf{\theta}_s$ (where the subindex $s$ refers to a sensor) be the parameter vector of a certain sensor. We can define this vector as:
%TODO thetas en negritas
\begin{equation}
\mathbf{\theta} = [k_{sx},k_{sy},k_{sy},b_{sx},b_{sy},b_{sy}, \alpha_{sxy},\alpha_{sxz},\alpha_{syx},\alpha_{syz},\alpha_{szx},\alpha_{szy}]^T
\label{eq:theta}
\end{equation}

In equation \ref{eq:theta}, $k_{si}$, with $i=1,2,3$ are the diagonal elements of the matrix $\mathbf{K}_s$, $b_{si}$, with $i = 1,2,3$ are the elements of vector $\mathbf{b}_s$ and $\alpha_{sij}$, with $i = 1,2,3$, $j = 1,2,3$ and $i \neq j$ are the elements outside the diagonal of the matrix $\mathbf{T}_s^p$.\\

As adjust criterium we choose to minimize the sum of the squares of the norms of the diferences between true accleracion and measured acceleration. This problem can be written as follows:

\begin{equation}
\min_\theta \sum_{i = 1}^M ||\mathbf{s}_i^p - \mathbf{T}_s^p(\mathbf{K_s})^{-1}(\tilde{\mathbf{s}}_i^s-\mathbf{b}_s) ||^2
\label{eq:calib_problem}
\end{equation}

In equation \ref{eq:calib_problem}, $M$ is the cardinal of the training set, $\mathbf{s}_i^p$ is the true magnitude (acceleration or angular speed) and $\tilde{\mathbf{s}}_i$ are the values given by the sensor.\\

It is important to consider that the function that we want to minimize will generally have more than one local minimum. Thus, we can only assure that the optimum found by algorithms is a local optimum. To ensure that the solution obtained is the desired one, we need to choose carefully the seed for the algorithm. Tipically we will choose a vector $\mathbf{\theta}_0$ that is close to the values of the unknow parameters.

%TODO Negritas
\subsubsection{Accelerometer}

\subsubsection{Gyroscope}

\subsection{Temperature adjust}
